Palmer amaranth (\emph{Amaranthus palmeri}) adaptation to agroecossystems

### 2021-08-09 Manuscript/Manuscript.Rmd
as

@@

>>>>

```{r fig5, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../data analysis/figures/Figure 4.png")
```

@@

```{r, Figure-5, ref.label = "fig5", echo = FALSE, message = FALSE, fig.height=9, fig.width=4, fig.align='center', fig.cap='Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second transplant timing (B)', out.width = "120mm", out.height = "180mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

### 2021-08-09 Manuscript/Manuscript.tex
as

Palmer amaranth height and biomass were performed with a linear mixed
model using \emph{lmer} function from ``lme4'' package (Bates et al.,
2015). Plant height and biomass were transformed to meet model
assumption of normality. In the model, agroecosystem (crop, soybean,
fallow) was the fixed effect and year nested with location the random
effects. Analysis of variance was performed with \emph{anova} function
from ``car'' package (Fox and Weisberg, 2018). Marginal means and
compact letter display were estimated with \emph{emmeans} and \emph{cld}
from packages ``emmeans'' and multcomp (Hothorn et al., 2008).

@@

>>>>

Palmer amaranth height and biomass were performed with a linear mixed
model using \emph{lmer} function from ``lme4'' package (Bates et al.,
2015). Plant height and biomass were transformed to meet model
assumption of normality. In the model, agroecosystem (crop, soybean,
fallow) was the fixed effect and year nested with location the random
effects. Analysis of variance was performed with \emph{anova} function
from ``car'' package (Fox and Weisberg, 2018). Marginal means and
compact letter display were estimated with \emph{emmeans} and \emph{cld}
from packages ``emmeans'' and ``multcomp'' (Hothorn et al., 2008).

@@

{\centering \includegraphics[width=120mm,height=180mm]{../data analysis/figures/Figure 4}

\caption{Cumulative flowering of Palmer amaranth at first and second transplant timing (A) and day of year of 10, 50, and 90 cumulative flowering at first and second transplant timing (B)}\label{fig:Figure-5}
\end{figure}
